---
title: "template_PatentSearch"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Reference :
https://www.r-bloggers.com/accessing-patent-data-with-the-patentsview-package/amp/

### query
```{r}
library(patentsview)
library(tidyverse)
library(RColorBrewer)
```
```{r}
# Your query has to use the PatentsView query language, which is a JSON-based syntax 
qry_1 <- '{"_gt":{"patent_year":2007}}'
search_pv(query = qry_1, fields = NULL)
```
* Or you can use the domain specific language (DSL) provided in the
patentsview package to help you write the query:
```{r}
qry_2 <- qry_funs$gt(patent_year = 2007)
qry_2
search_pv(query = qry_2)
```
### fields
```{r}
search_pv(
  query = qry_funs$gt(patent_year = 2017),
  fields = c("patent_abstract", "patent_average_processing_time",
             "inventor_first_name", "inventor_total_num_patents")
)
```
* The fields that you can retrieve depends on the endpoint that you are
hitting. We've been using the "patents" endpoint thus far, so all of
these are retrievable:
```{r}
search_pv(
  query = qry_funs$gt(patent_year = 2007),
  fields = get_fields(endpoint = "patents", groups = c("patents", "inventors"))
)
```
## Example
* Patents in this area relate to "network architectures or network
communication protocols for separating internal from external
traffic." 

### Download the data
```{r}
# Write a query:
query <- with_qfuns( # with_qfuns is basically just: with(qry_funs, ...)
  and(
    begins(cpc_subgroup_id = 'H04L63/02'),
    gte(patent_year = 2007)
  )
)

# Create a list of fields:
fields <- c(
  c("patent_number", "patent_year"),
  get_fields(endpoint = "patents", groups = c("assignees", "cpcs"))
)
```
```{r}
# Send HTTP request to API's server:
pv_res <- search_pv(query = query, fields = fields, all_pages = TRUE)
```
### See where the patents are coming from (geographically)
```{r}
library(leaflet)
library(htmltools)
library(dplyr)
library(tidyr)
```
```{r}
data <-
  pv_res$data$patents %>%
    unnest(assignees) %>%
    select(assignee_id, assignee_organization, patent_number,
           assignee_longitude, assignee_latitude) %>%
    group_by_at(vars(-matches("pat"))) %>%
    mutate(num_pats = n()) %>%
    ungroup() %>%
    select(-patent_number) %>%
    distinct() %>%
    mutate(popup = paste0("< color='Black'>",
                          htmlEscape(assignee_organization), "<br><br>Patents:",
                          num_pats, "<>")) %>%
    mutate_at(vars(matches("_l")), as.numeric) %>%
    filter(!is.na(assignee_id))
```
```{r}
leaflet(data) %>%
  addProviderTiles(providers$CartoDB.DarkMatterNoLabels) %>%
  addCircleMarkers(lng = ~assignee_longitude, lat = ~assignee_latitude,
                   popup = ~popup, ~sqrt(num_pats), color = "yellow")
```
### Plot the growth of the field's topics over time
```{r}
data <-
  pv_res$data$patents %>%
    unnest(cpcs) %>%
    filter(cpc_subgroup_id != "H04L63/02") %>% # remove patents categorized into only top-level category of H04L63/02
    mutate(
      title = case_when(
        grepl("filtering", .$cpc_subgroup_title, ignore.case = T) ~
          "Filtering policies",
        .$cpc_subgroup_id %in% c("H04L63/0209", "H04L63/0218") ~
          "Architectural arrangements",
        grepl("Firewall traversal", .$cpc_subgroup_title, ignore.case = T) ~
          "Firewall traversal",
        TRUE ~
          .$cpc_subgroup_title
      )
    ) %>%
    mutate(title = gsub(".*(?=-)-", "", title, perl = TRUE)) %>%
    group_by(title, patent_year) %>%
    count() %>%
    ungroup() %>%
    mutate(patent_year = as.numeric(patent_year))

ggplot(data = data) +
  geom_smooth(aes(x = patent_year, y = n, colour = title), se = FALSE) +
  scale_x_continuous("\nPublication year", limits = c(2007, 2016),
                     breaks = 2007:2016) +
  scale_y_continuous("Patents\n", limits = c(0, 700)) +
  scale_colour_manual("", values = brewer.pal(5, "Set2")) +
  theme_bw() + # theme inspired by https://hrbrmstr.github.io/hrbrthemes/
  theme(panel.border = element_blank(), axis.ticks = element_blank())
```
# Following examples are from :
https://ropensci.github.io/patentsview/articles/examples.html

### Patents endpoint
```{r}
library(patentsview)
# Which patents have been cited by more than 500 US patents?
search_pv(query = qry_funs$gt(patent_num_cited_by_us_patents = 500))
```
```{r}
# How many distinct inventors are represented by these highly-cited patents?
# Setting subent_cnts = TRUE will give us the subentity counts. Since inventors 
# are subentities for the patents endpoint, this means we will get their counts.
search_pv(
  query = qry_funs$gt(patent_num_cited_by_us_patents = 500),
  fields = c("patent_number", "inventor_id"), 
  subent_cnts = TRUE
)

```
```{r}
# Where geographically have Microsoft inventors been coming from over the past 20 years?
# Write the query
query <- with_qfuns(
  and(
    gte(patent_date = "2007-07-25"), # Dates are in yyyy-mm-dd format 
    contains(assignee_organization = "microsoft")
  )
)

# Create a field list
inv_fields <- get_fields(endpoint = "patents", groups = "inventors")
fields <- c(inv_fields, "patent_number")

# Pull the data
pv_out <- search_pv(query, fields = fields, all_pages = TRUE)

# Unnest the inventor list column
unnest_pv_data(pv_out$data, "patent_number")
```
### Inventors endpoint
```{r}
# Which inventors have Chicago, IL listed as their location on at least one patent
search_pv(
  query = '{"_and":[{"location_city":"Chicago"},{"location_state":"IL"}]}',
  endpoint = "inventors"
)
```
### Assignees endpoint
```{r}
# Which assignees have an interest in beer?
search_pv(
  query = qry_funs$text_phrase(patent_title = "beer"), 
  endpoint = "assignees"
)
```
## Getting started
### A basic example
https://ropensci.github.io/patentsview/articles/getting-started.html
```{r}
library(patentsview)

search_pv(
  query = '{"_gte":{"patent_date":"2007-01-01"}}',
  endpoint = "patents"
)

```
### Writing queries
```{r}
qry_funs$gte(patent_date = "2007-01-01")
```
```{r}
with_qfuns(
  and(
    gte(patent_date = "2007-01-01"),
    text_phrase(patent_abstract = c("computer program", "dog leash"))
  )
)
```
### Fields
```{r}
search_pv(
  query = '{"_gte":{"patent_date":"2007-01-01"}}',
  fields = c("patent_number", "patent_title")
)
```
* To list all of the retrievable fields for a given endpoint, use get_fields():
```{r}
retrvble_flds <- get_fields(endpoint = "patents")
head(retrvble_flds)
```
### Paginated responses
```{r}
search_pv(
  query = qry_funs$eq(inventor_last_name = "chambers"),
  page = 2, per_page = 150 # gets records 150 - 300
) 
#>
```
* You can download all pages of output in one call by setting all_pages = TRUE. 
```{r}
search_pv(
  query = qry_funs$eq(inventor_last_name = "chambers"),
  all_pages = TRUE
)
```
### 7 endpoints for 7 entities
```{r}
query <- qry_funs$eq(inventor_last_name = "chambers")
fields <- c("patent_number", "inventor_last_name", "assignee_organization")

# Here we are using the patents endpoint:
search_pv(query, endpoint = "patents", fields = fields)
```
```{r}
# While here we are using the assignees endpoint:
search_pv(query, endpoint = "assignees", fields = fields)
```
### Casting fields
```{r}
res <- search_pv(
  query = "{\"patent_number\":\"5116621\"}", 
  fields = c("patent_date", "patent_title", "patent_year")
)

res
```
```{r}
# Use more appropriate data types:
cast_pv_data(res$data)
```
### FAQs
```{r}
query <- with_qfuns(text_any(patent_abstract = 'tool animal'))
```
```{r}
query_1a <- with_qfuns(
  and(
    text_any(patent_abstract = 'tool animal'),
    lte(patent_date = "2010-01-01")
  )
)

query_1b <- with_qfuns(
  and(
    text_any(patent_abstract = 'tool animal'),
    gt(patent_date = "2010-01-01")
  )
)
```
* How do I access the data frames inside the list columns returned by search_pv()?
```{r}
# Create field list
asgn_flds <- c("assignee_id", "assignee_organization")
subent_flds <- get_fields("assignees", c("applications", "gov_interests"))
fields <- c(asgn_flds, subent_flds)

# Pull data
res <- search_pv(
  query = qry_funs$contains(inventor_last_name = "smith"), 
  endpoint = "assignees", 
  fields = fields
)
res$data
```
* res$data has vector columns for those fields that belong to the primary entity (e.g., res$data$assignees$assignee_id) and list columns for those fields that belong to any secondary entity (e.g., res$data$assignees$applications). You have two good ways to pull out the data frames that are nested inside these list columns:

* Use tidyr::unnest. (This is probably the easier choice of the two).
```{r}
library(tidyr)

# Get assignee/application data:
res$data$assignees %>% 
  unnest(applications) %>%
  head()
```
```{r}
# Get assignee/gov_interest data:
res$data$assignees %>% 
  unnest(gov_interests) %>%
  head()
```
* Use patentsview::unnest_pv_data. unnest_pv_data() creates a series of data frames (one for each entity level) that are like tables in a relational database. You provide it with the data returned by search_pv() and a field that can act as a unique identifier for the primary entities:
```{r}
unnest_pv_data(data = res$data, pk = "assignee_id")
```

